A Study on Penguins: A Minimal Reproducible Example

### 2024-08-21 01_Example/Manuscript.qmd
Use violin plot rather than box plot
Friends don't let friends use box plots

```{r}
#| label: "bill-length-comparison"
#| echo: false
#| fig.cap: "Histogram with Scatter Plot of Bill Lengths by Sex"

# Create ggplot object
ggplot2::ggplot(data_clean, ggplot2::aes(x = sex, y = bill_length_mm, fill = sex), group = sex) +
  ggplot2::geom_boxplot(width = 0.5, show.legend = FALSE) +
  ggplot2::geom_jitter(width = 0.15, show.legend = FALSE) +
  ggplot2::labs(x = "Sex", y = "Bill length in mm") +
  ggplot2::theme_minimal()
```

>>>>

```{r}
#| label: "bill-length-comparison"
#| echo: false
#| fig-cap: "Scatter Plot of Bill Lengths by Sex"
#| fig-subcap: "Violin Plot Displays Quartiles"

# Create ggplot object
ggplot2::ggplot(data_clean, ggplot2::aes(x = sex, y = bill_length_mm, fill = sex), group = sex) +
  ggplot2::geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    show.legend = FALSE
  ) +
  ggplot2::geom_jitter(width = 0.15, show.legend = FALSE) +
  ggplot2::labs(x = "Sex", y = "Bill length in mm") +
  ggplot2::theme_minimal()
```
